Active Learning for SAT Solver Benchmarking

### 2022-10-10 paper/paper.tex
Revise Section 3.1 (Incremental Benchmarking Framework)
Rewording for clarity and language.

In this section, we present the details of our approach.
Section~\ref{sec:main-framework} describes the general procedure.
Section~\ref{sec:main-model} specifies the details of the underlying prediction model and discusses how we may derive a solver ranking from that model.
Possible criteria for sampling instances are discussed in Section~\ref{sec:main-sampling}.
Section~\ref{sec:main-stopping} concludes with possible stopping conditions.

@@

Our framework follows a simple three-step schema.
Algorithm~\ref{algALBenchmark} outlines the procedure. 
While the stopping condition is not met (line~1), we select \emph{one} problem instance from the pool of instances (line~2) and evaluate the new solver $\hat{a}$ on it (line~3).
We then use the acquired result to update the model (line~4).
When the stopping criterion is met, we return the predicted score of the given solver $\hat{a}$.

Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark by one instance at a time rather than using batches which is also proposed in current active-learning advances~\cite{SinhaED19,2019gaal}.

@@

  \While{$\operatorname{not} \, \operatorname{stop}\!\left(\mathcal{M}\right)$}{
    $s \leftarrow \operatorname{selectNextInstance}\!\left(\mathcal{M}\right)$

@@

    $\operatorname{updateModel}\!\left(\mathcal{M},\, s,\, t\right)$
  }

  \Return $\operatorname{predictScore}\!\left(\mathcal{M}, \hat{a}\right)$

>>>>

In this section, we present the details of our approach.
Section~\ref{sec:main-framework} describes the general framework.
Section~\ref{sec:main-model} specifies the details of the underlying prediction model and describes how we may derive a solver ranking from that model.
We discuss possible criteria for sampling instances in Section~\ref{sec:main-sampling}.
Section~\ref{sec:main-stopping} concludes with possible stopping conditions.

@@

Our framework to score a new solver~$\hat{a}$ follows a simple three-step procedure, outlined in Algorithm~\ref{algALBenchmark}:
While the stopping condition is not met (line~1), we select \emph{one} problem instance from the pool of instances with the help of a prediction model~$\mathcal{M}$ (line~2) and evaluate the new solver~$\hat{a}$ on this instance (line~3).
We then use the acquired result to update the prediction model~$\mathcal{M}$ (line~4).
When the stopping criterion is met, we return the predicted score of the new solver~$\hat{a}$ (line~5).

Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark by one instance at a time rather than using batches, which is also proposed in current active-learning advances~\cite{SinhaED19,2019gaal}.

@@

  \While(\tcp*[f]{cf. Section~\ref{sec:main-stopping}}){$\operatorname{not} \, \operatorname{stop}\!\left(\mathcal{M}\right)$}{
    $s \leftarrow \operatorname{selectNextInstance}\!\left(\mathcal{M}\right)$ \tcp*{cf. Section~\ref{sec:main-sampling}}

@@

    $\operatorname{updateModel}\!\left(\mathcal{M},\, s,\, t\right)$ \tcp*{cf. Section~\ref{sec:main-model}}
  }

  \Return $\operatorname{predictScore}\!\left(\mathcal{M}\right)$ \tcp*{cf. Section~\ref{sec:main-model}}
